---
title: "STA160-allcom_plots"
author: "Shih-Chi Chen"
date: "6/1/2022"
output:
  pdf_document: default
  html_document: default
---

```{r}
#import weather data combined fire data
joined_weather <- read.csv("~/Downloads/ClimateAnalysis-main/joined_weather.csv")
```

```{r}
#change type to date
joined_weather$Date <- as.Date(joined_weather$Date)
```

## EDA for weather data

```{r}
# load the library
library(ggplot2)
library(ggridges)
```

# Scatter plots
```{r}
#wind vs temp
ggplot(data = joined_weather) +
  geom_point(mapping = aes(x = average_left, y = wind_speed, colour = county))
```
```{r}
#precip vs wind
ggplot(data = joined_weather) +
  geom_point(mapping = aes(x = Precip_right, y = wind_speed, colour = county))
```
```{r}
#precip vs avg temp
ggplot(data = joined_weather) +
  geom_point(mapping = aes(x = Precip_right, y = average_left, colour = county))
```

# Distribution plots
```{r}
#county and average temp
theme_set(theme_ridges())
ggplot(joined_weather, aes(x = average_left, y =county )) +
  geom_density_ridges(aes(fill = county)) 
```

```{r}
#county and wind speed
theme_set(theme_ridges())
ggplot(joined_weather, aes(x = wind_speed, y =county )) +
  geom_density_ridges(aes(fill = county)) 
```

```{r}
#county and Precip
theme_set(theme_ridges())
ggplot(joined_weather, aes(x = Precip_right, y =county )) +
  geom_density_ridges(aes(fill = county)) 
```

## EDA for fire and weather data

```{r}
#import weather data combined fire data
weather_fire <- read.csv("~/Downloads/ClimateAnalysis-main/weather_fire.csv")
#change type to date
weather_fire$Date <- as.Date(weather_fire$Date)
weather_fire$date.CONT_DATE.<- as.Date(weather_fire$date.CONT_DATE.)

#fire days
days=weather_fire$date.CONT_DATE.-weather_fire$Date
#add to df
weather_fire$cts_days=days
```

#Boxplots 
From the boxplot, it shows that the large fire tend to have high wind speed.
```{r}
#wind speed vs fire size class
ggplot(data = weather_fire, mapping = aes(x = FIRE_SIZE_CLASS, y = wind_speed)) + 
  geom_boxplot()
```

From the plot, it shows that most of the reason for fires occur in the low wind speed(<10). However, the Equipment Use and Debris Burning tend to causes fires when wind speed is large than 10. There also can be seen that the range of wind speed is large when the fire was caused by  Arson and Debris Burning.

```{r}
#wind speed vs fire cause
ggplot(data = weather_fire, mapping = aes(x = STAT_CAUSE_DESCR, y = wind_speed)) + 
   theme(legend.position="none") +
  geom_boxplot()+
  coord_flip()
```

# bar chart
```{r}
#wind speed, fips and fire size class bar
ggplot(data=weather_fire, aes(x=FIPS_NAME, y=wind_speed, fill=FIRE_SIZE_CLASS)) +
  geom_bar(stat="identity", position=position_dodge())
```

```{r}
# #wind speed, fips and cause
ggplot(data=weather_fire, aes(x=FIPS_NAME, y=wind_speed, fill=STAT_CAUSE_DESCR)) +
geom_bar(stat="identity", position=position_dodge())

```
```



